Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing

### 2018-05-05 paper.tex
New subsection in introduction to describe project purpose.

\section{Introduction}
Background/history of this research topic, goals for this section

@@

>>>>

\section{Introduction}
Two commonly used density profiles in weak gravitational lensing are the isothermal profile and the Navarro-Frenk-White (NFW) profile.

@@

\subsection{Project Purpose}
The goal of this project is to devise a method to analyze lensed galaxy cluster data and find which density profile is more probable between the isothermal and NFW profiles.
